A Case Study in Preserving a High Energy Physics Application

### 2014-03-13 paper.tex
add conclusion

In this paper, we tries to illustrate the challenges involved in data and software preservation and reproduction through one case study in preserving one High Energy Physics application.
Four different solutions to repeat the original application, together with the pros and cons of each one, are proposed and analyzed. Each new solution aims to improve the reproductivity of the application and reduce the complexity of reproduction. Finally, we propose one fine-grained packaging toolkit to help the original author to generate one independent package containing all the necessary dependencies

>>>>

In this paper, we tries to illustrate the challenges involved in data and software preservation and reproduction through one case study in preserving one High Energy Physics application.
Four different solutions to repeat the original application, together with the pros and cons of each one, are proposed and analyzed. Each new solution aims to improve the reproductivity of the application and reduce the complexity of reproduction. Finally, we propose one fine-grained packaging toolkit to help the original author to generate one independent package containing all the necessary dependencies except for common dependencies, and repeat the experiment from scratch on two Amazon EC2 virtual machines successfully.

In the future, more case studies will be investigated to verify the correctness of our packaging toolkit. The challenges we propose in this paper will also be investigated.
